Joint analysis of read count data

### 2020-09-09 combined_analysis/combine_all_data.Rmd
add zenith

run_zenith = function(fit, coefs, gs.collection, n_genes_mi=10, n_genes_max=5000){

@@

>>>>

run_zenith = function(fit, coefs, gs.collection, n_genes_min=10, n_genes_max=5000){

@@

```{r show.gene_set_test.marginal}
res_zenith_marginal.GO[['Scz']][1:20,] %>% kable(caption="Scz") %>% kable_styling(full_width=FALSE)
res_zenith_marginal.GO[['BP']][1:20,] %>% kable(caption="BP") %>% kable_styling(full_width=FALSE)
res_zenith_marginal.GO[['Scz']][1:Sex,] %>% kable(caption="Sex") %>% kable_styling(full_width=FALSE)

```
